Screening Sinkhorn Algorithm for Regularized Optimal Transport

### 2019-05-20 tex/v3/appendix.tex
expe

\begin{figure*}[t]
	\centering
	%~\hfill~	\includegraphics[width=6.cm]{../../figure/da_toy_problem.pdf}~\hfill~\\
	~\hfill~\includegraphics[width=6.cm]{../../figure/wda_accur_toy.pdf}~\hfill~
	\includegraphics[width=6.cm]{../../figure/wda_accur_mnist.pdf}~\hfill~\\
	\caption{Accuracy of a $1$-nearest-neighbour after WDA for the (left) toy problem.
		(right) MNIST). We note a slight loss of performance for the toy problem, whereas for MNIST, all approaches yield the same performance. 
		\label{fig:wda_gain}}
\end{figure*}

\begin{figure*}[t]
	\centering
	%~\hfill~	\includegraphics[width=6.cm]{../../figure/da_toy_problem.pdf}~\hfill~\\
	~\hfill~\includegraphics[width=6.cm]{../../figure/da_toy_problem.pdf}~\hfill~
	\includegraphics[width=6.cm]{../../figure/da_accur_toy_regcl100.pdf}~\hfill~\\
	~\hfill~\includegraphics[width=6.cm]{../../figure/da_time_toy_regcl100.pdf}
	~\hfill~\includegraphics[width=6.cm]{../../figure/da_gain_toy_regcl100.pdf}~\hfill~\\
	\caption{OT Domain Adaptation on a 3-class Gaussian toy problem. (top-left) Examples of source and target samples. (top-right) Evolution of the accuracy of a 1-nearest-neighbour classifier with respect to the number of samples. (bottom-left) Running time of the \emph{Sinkhorn} and \emph{Screenkhorn} for different decimation
	factors. (bottom-right). Gain in computation time. This toy problem is a problem in which classes are overlapping and distance between samples are rather limited. According to our analysis, this may be a situation in which \emph{Screenkhorn} may
	result in smaller computational gain. We can remark that with respect to the accuracy
	\emph{Screenkhorn} with decimation factors up to $10$ are competitive with \emph{Sinkhorn}, although a slight loss of performance. Regarding computational time, for this example, small decimation factors does not  result in gain. However for above  $5$-factor decimation, the gain goes from  $2$ to $10$ depending on
	the number of samples. 
	\label{fig:otda}}
\end{figure*}

>>>>

\begin{figure*}[t]
	\centering
	%~\hfill~	\includegraphics[width=6.cm]{./figs/da_toy_problem.pdf}~\hfill~\\
	~\hfill~\includegraphics[width=6.cm]{./figs/wda_accur_toy.pdf}~\hfill~
	\includegraphics[width=6.cm]{./figs/wda_accur_mnist.pdf}~\hfill~\\
	\caption{Accuracy of a $1$-nearest-neighbour after WDA for the (left) toy problem.
		(right) MNIST). We note a slight loss of performance for the toy problem, whereas for MNIST, all approaches yield the same performance. 
		\label{fig:wda_gain}}
\end{figure*}

\begin{figure*}[t]
	\centering
	%~\hfill~	\includegraphics[width=6.cm]{./figs/da_toy_problem.pdf}~\hfill~\\
	~\hfill~\includegraphics[width=6.cm]{./figs/da_toy_problem.pdf}~\hfill~
	\includegraphics[width=6.cm]{./figs/da_accur_toy_regcl100.pdf}~\hfill~\\
	~\hfill~\includegraphics[width=6.cm]{./figs/da_time_toy_regcl100.pdf}
	~\hfill~\includegraphics[width=6.cm]{./figs/da_gain_toy_regcl100.pdf}~\hfill~\\
	\caption{OT Domain Adaptation on a 3-class Gaussian toy problem. (top-left) Examples of source and target samples. (top-right) Evolution of the accuracy of a 1-nearest-neighbour classifier with respect to the number of samples. (bottom-left) Running time of the \emph{Sinkhorn} and \emph{Screenkhorn} for different decimation
	factors. (bottom-right). Gain in computation time. This toy problem is a problem in which classes are overlapping and distance between samples are rather limited. According to our analysis, this may be a situation in which \emph{Screenkhorn} may
	result in smaller computational gain. We can remark that with respect to the accuracy
	\emph{Screenkhorn} with decimation factors up to $10$ are competitive with \emph{Sinkhorn}, although a slight loss of performance. Regarding computational time, for this example, small decimation factors does not  result in gain. However for above  $5$-factor decimation, the gain goes from  $2$ to $10$ depending on
	the number of samples. 
	\label{fig:otda}}
\end{figure*}
